Figures for Paper

### 2021-09-22 paper_figures.Rmd
Update paper_figures.Rmd
fix color

ggplot(df2, aes(x = experiment, fill = RNA, y = mean_kd)) +
    geom_bar(stat="identity", position="dodge") +
    #geom_point(aes(group=RNA), position="dodge") +
    geom_errorbar(aes(x=experiment, ymin = mean_kd-sd2, ymax = mean_kd+sd2,
                      fill = RNA), position="dodge") +
    ylim(0, NA) +
    ggpubr::theme_pubr() +
    ylab("Kd / nM") +
    xlab("")

>>>>

ggplot(df2, aes(x = experiment, fill = RNA, y = mean_kd)) +
    geom_bar(stat="identity", position="dodge") +
    #geom_point(aes(group=RNA), position="dodge") +
    geom_errorbar(aes(x=experiment, ymin = mean_kd-sd2, ymax = mean_kd+sd2,
                      fill = RNA), position="dodge") +
    ylim(0, NA) +
    ggpubr::theme_pubr() +
    ylab("Kd / nM") +
    xlab("") +
  scale_fill_manual(values = c("#0c9bbdff","#ffb700ff"))
